### 2025-06-08 question_papers/aima104_first_in_sem.tex
question aima104

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: II \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 2mm
\rule{\textwidth}{1pt}
\hskip 15mm \textit{Write the answer according to the mark allocated to it}. \textit{For short questions, write short answers, for long questions write long answers}.

@@

\begin{questions}

\question Round off the digits 45.321 and 12.987 upto two decimal places and find the error in their product after rounding off. [2]

\question

>>>>

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 104 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 2mm
\rule{\textwidth}{1pt}
\hskip 15mm \textit{Write the answer according to the mark allocated to it}. \textit{For short questions, write short answers, for long questions write long answers}.

@@

\begin{questions}
\question For a matrix $A$ of order $m \times n$. Show that $Null(A)$ is a subspace of $\mathbb{R}^n$. [2]

  \question Show that the transformation $T(x)=x+3$ is not linear. [2]

  \question Describe the transformation of the following matrix geometrically:
  $\begin{bmatrix}
    1 & 0\\
    0 & 0
  \end{bmatrix}$. [2]

\question Prove: The transformation $T: V \to W$ is linear, then $T(0)=0$. [2]

  \question Verify Rank Nullity Theorem: $\displaystyle \begin{bmatrix}
    1 & 2 & 3 \\
    6 & 5 &4 \\
    7 & 8 & 9
\end{bmatrix}.$ [4]

\question Show that the transformation that rotates each point in $\mathbb{R}^2$, about the origin, through an angle $\phi$ counterclockwise, is a linear transformation by find the standard matrix of the transformation. [4]

\question Solve: \hspace{2mm} $x_2+4x_3 = -5, \hspace{5mm} x_1+3x_2+5x_3 = -2, \hspace{5mm} 3x_1 + 7x_2 + 7x_3 = 6$. [4]

### 2025-06-08 question_papers/aima104_mcq_first_in_sem.tex
question aima104

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: II \\
    Time: 15 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 10
  \end{flushleft}
\end{minipage}
\vspace{-8mm}
\begin{center}
  \rule{\textwidth}{1pt}
  Roll No: \hspace{5.5cm} Marks Scored:
  \vskip -3mm
\rule{\textwidth}{1pt}
\end{center}

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
  \question Give an example of an approximate value: \rule{8cm}{0.15mm}.

  \question Write the number of significant digits in 20300.00  \rule{5cm}{0.15mm}.

  \question Write the precision of 45.203 \rule{5cm}{0.15mm}.

  \question Write the accuracy of 7953.2300 \rule{5cm}{0.15mm}.

\end{questions}

>>>>

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 15 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 10
  \end{flushleft}
\end{minipage}
\vspace{-8mm}
\begin{center}
  \rule{\textwidth}{1pt}
  Roll No: \hspace{5.5cm} Marks Scored:
  \vskip -3mm
\rule{\textwidth}{1pt}
\end{center}

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
\question Give an example of a vector and its scalar. \rule{7cm}{0.15mm}.
\question Give an example of a subspace of $\mathbb{R}^2$ : \rule{8cm}{0.15mm}.

\question Give an example of $3 \times 4 $ row echelon for matrix. \rule{7cm}{0.15mm}.

\question Find the rank of the matrix $\displaystyle \begin{bmatrix}
    1 & 3 & 5 \\
    2 & 6 & 10 \\
    4  & 12 & 20
\end{bmatrix}.$ \rule{7cm}{0.15mm}.

\question Determine whether the system has unique solution, no unique solution or no solution. $ \left[ \begin{matrix}
    1 & 0  \\
    0 & 1  \\
    0 & 0
\end{matrix} \;\; \vline \;\;
\begin{matrix}
    0\\ 0\\ -1
\end{matrix} \right]$ \rule{7cm}{0.15mm}.

\question Write the basis of the vector space ${0}$. \rule{7cm}{0.15mm}.

 \question Suppose a $4 \times 7$ matrix $A$ has four pivot columns. Is $Col(A) = \mathbb{R}^4$? Is $Nul(A) = \mathbb{R}^3$ ?
\end{questions}
